---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DrugExposureDiagnostics

<!-- badges: start -->
<!-- badges: end -->

The goal of DrugExposureDiagnostics is to summarise ingredient specific drug exposure data in the OMOP CDM.

## Installation

You can install the development version of DrugExposureDiagnostics like this:

``` r
install.packages("remotes")
remotes::install_github("darwin-eu-dev/DrugExposureDiagnostics")
```
## Setup

In order to use the example data from the eunomia dataset, you need to set an environment variable. You can do it like this:

* ```{r} usethis::edit_r_environ() ```
* EUNOMIA_DATA_FOLDER = "/mypath/eunomiaData"
* save the file
* restart RStudio

## Example use
```{r, message=FALSE}
library(DrugExposureDiagnostics)
library(CDMConnector)
library(dplyr)
```

```{r}
cdm <- getEunomiaCdm()
```

Let´s look at the ingredient acetaminophen (https://athena.ohdsi.org/search-terms/terms/1125315).

We can run all the checks available in ´DrugExposureDiagnostics´ using the ´executeChecks´ function. 

```{r}
all_checks <- executeChecks(cdm, 1125315, minCellCount = NULL)
```

The output is a list which contains the following set of tibbles:
```{r}
names(all_checks)
```

The first item contains information on the concept ids that are used in the database for a given ingredient. 
```{r}
glimpse(all_checks$conceptSummary)
all_checks$conceptSummary %>% 
  select("drug_concept_id", "drug")
```

Other tibbles then contain information from the various checks performed.

For example, we can see a summary of missingness for the ingredient-related records in the  drug exposure table, both overall and by concept.
```{r}
all_checks$missingValuesOverall
all_checks$missingValuesByConcept
```

Or we can also see a summary of drug exposure duration (drug_exposure_end_date - drug_exposure_end_date + 1), again overall or by concept.
```{r}
all_checks$drugExposureDurationOverall
all_checks$drugExposureDurationByConcept
```

For further information on the checks performed please see the package vignettes.

After running the checks we can write the CSVs to disk using the `writeResultToDisk` function.
```{r}
writeResultToDisk(all_checks,
                  databaseId = "Synthea", 
                  outputFolder =tempdir())
```


```{r, echo=FALSE}
  DBI::dbDisconnect(attr(cdm, "dbcon"), shutdown = TRUE)
```
