---
title: "Days Supply"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Days Supply}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Run the days supply check 
```{r setup}
library(DrugExposureDiagnostics)
library(dplyr)
library(DT)

# acetaminophen concept id is 1125315
acetaminophen <- 1125315
cdm <- mockDrugExposure()
acetaminophen_checks <- executeChecks(cdm = cdm, 
                                      ingredients = acetaminophen, 
                                      checks = "daysSupply")
```

## Days supply Overall
This shows the days supply of the drug records summarised on ingredient level.

```{r}
datatable(acetaminophen_checks$drugDaysSupply,
  rownames = FALSE
)
```

| Column  | Description |
:------------- | :------------- |
ingredient_concept_id | Concept ID of ingredient. |
ingredient  | Name of drug ingredient. |
n_records | Number of records for ingredient concept. If n_records is the same as n_sample this means that there are more records but the number was cut at the pre-specified sample number for efficiency reasons. |
n_sample | The pre-specified maximum sample. If n_records is smaller than the sample it means that sampling was ignored because the total number of records was already too small. |
n_person | Number of individuals. |
minimum_drug_exposure_days_supply  | Minimum drug exposure days supply |
q05_drug_exposure_days_supply_supply  | 5th quantile of drug exposure days supply |
q10_drug_exposure_days_supply  | 10th quantile of drug exposure days supply |
q25_drug_exposure_days_supply   | 25th quantile of drug exposure days supply |   
median_drug_exposure_days_supply  | Median drug exposure days supply |
q75_drug_exposure_days_supply  | 75th quantile of drug exposure days supply |
q90_drug_exposure_days_supply  | 90th quantile of drug exposure days supply |
q95_drug_exposure_days_supply  | 95th quantile of drug exposure days supply |
maximum_drug_exposure_days_supply  | Maximum drug exposure days supply |
n_different_days_supply_and_drug_dates | Number of records where days supply differs to drug exposure days supply (estimated through drug_exposure_end_date - drug_exposure_start_date + 1). Ideally these two values should overlap because often the drug_exposure_end_date is derived from the days_supply field. However, the days_supply field is not a required field where as drug_exposure_end_date is a required field. If days_supply is missing then it is automatically captured as a difference. |
n_days_supply_match_drug_dates | Number of records where days supply is identical to drug exposure days supply (estimated through drug_exposure_end_date - drug_exposure_start_date + 1). Ideally these two values should overlap because often the drug_exposure_end_date is derived from the days_supply field. However, the days_supply field is not a required field where as drug_exposure_end_date is a required field. |
n_missing_days_supply | Number of records with missing days supply. This field together with n_different_days_supply_and_drug_dates and n_days_supply_match_drug_dates shall be identical to n_records. |
proportion_different_days_supply_and_drug_dates | Proportion of records where days supply differs to drug exposure days supply (estimated through drug_exposure_end_date - drug_exposure_start_date + 1). |
proportion_days_supply_match_drug_dates | Proportion of records where days supply is idential to drug exposure days supply (estimated through drug_exposure_end_date - drug_exposure_start_date + 1). |      Proportion of records with missing values in days_supply.  This field together with proportion_different_days_supply_and_drug_dates and proportion_days_supply_match_drug_dates shall add up to 1. |
proportion_missing_days_supply | 
result_obscured | TRUE if count has been suppressed due to being below the minimum cell count, otherwise FALSE. | 

## Days supply by drug concept
This shows the days supply on the drug concept level. The tables are identical to the overall just including two more columns at the beginning. \


| Column  | Description |
:------------- | :------------- |
drug_concept_id  | ID of the drug concept. |
drug  | Name of the drug concept. |

```{r}
datatable(acetaminophen_checks$drugDaysSupplyByConcept,
  rownames = FALSE
)
```

