---
title: "Drug Types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DrugTypes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Run the drug type check
The name drug type may be misleading. It refers to whether the drugs records are prescriptions or claims or similar. The whole list of drug types can be seen in athena. https://athena.ohdsi.org/search-terms/terms?conceptClass=Drug+Type&invalidReason=Valid&page=1&pageSize=15&query=&boosts

```{r setup}
library(DrugExposureDiagnostics)
library(dplyr)
library(DT)

# acetaminophen concept id is 1125315
acetaminophen <- 1125315
cdm <- mockDrugExposure()
acetaminophen_checks <- executeChecks(
  cdm = cdm,
  ingredients = acetaminophen,
  checks = "type"
)
```

## Drug Type Overall
This shows the drug type of the drug records summarised on ingredient level.

```{r}
datatable(acetaminophen_checks$drugTypesOverall,
  rownames = FALSE
)
```

| Column  | Description |
:------------- | :------------- |
ingredient_concept_id | Concept ID of ingredient. |
ingredient  | Name of drug ingredient. |
drug_type_concept_id  | Concept ID of drug type |  
drug_type  | Concept name for drug type |     
n_records | Number of records for ingredient concept. If n_records is the same as n_sample this means that there are more records but the number was cut at the pre-specified sample number for efficiency reasons. |
n_sample | The pre-specified maximum sample. If n_records is smaller than the sample it means that sampling was ignored because the total number of records was already too small. |
n_person | Number of individuals. |
result_obscured | TRUE if count has been suppressed due to being below the minimum cell count, otherwise FALSE. |


## Drug Type by drug concept
This shows the drug type of the drug records on the drug concept level. The tables are identical to the overall just including two more columns at the beginning. \


| Column  | Description |
:------------- | :------------- |
drug_concept_id  | ID of the drug concept. |
drug  | Name of the drug concept. |

```{r}
datatable(acetaminophen_checks$drugTypesByConcept,
  rownames = FALSE
)
```
