---
title: "Introduction To DrugExposureDiagnostics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_DrugExposureDiagnostics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r , include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

```{r setup,message= FALSE, warning=FALSE}
library(DrugExposureDiagnostics)
library(CDMConnector)
library(dplyr)
library(DT)
```
First, connect to the database.

```{r}
cdm <- getEunomiaCdm()
```

### Check for single ingredient. 

In the DrugExposureDiagnostics package, all the diagnostics are conducted on ingredient level. We will use "acetaminophen" as an example. Here is a brief look at this ingredient. 

+------------------+---------------+
| Property         | Value         |
+------------------+---------------+
| Concept Name     | acetaminophen |
+------------------+---------------+
| Domain ID        | Drug          |
+------------------+---------------+
| Concept Class ID | Ingredient    |
+------------------+---------------+
| Vocabulary ID    | RxNorm        |
+------------------+---------------+
| Concept ID       | 1125315       |
+------------------+---------------+
| Concept code     | 161           |
+------------------+---------------+
| Validity         | Valid         |
+------------------+---------------+
| Concept          | Standard      |
+------------------+---------------+
| Valid start      | 01-Jan-1970   |
+------------------+---------------+
| Valid end        | 31-Dec-2099   |
+------------------+---------------+

We can run all available checks at the same time using the ´executeChecks()´ function. This will return a list which contains the results of each check.

```{r eval=FALSE}
executeChecks(cdm,
              ingredients = c(1125315),
              subsetToConceptId = NULL,
              checks = c("missing", "exposureDuration", "type", "route","sourceConcept", "daysSupply", "verbatimEndDate","dailyDose", "sig", "quantity", "histogram"), 
              minCellCount = 5,
              sample = 1000000,
              verbose = FALSE
)
```

The`cdm` is the database reference of the OMOP CDM using the `CDMConnector` package.    
The `ingredients` is a list of ingredients of interests, by default it is 1125315 for acetaminophen. 
The `subsetToConceptId` is a vector of drug concept ID's to subset down to.
`checks` allows to select the checks to be executed, by default, all the checks will be run.   
`sample` is the number of samples, by default, 1 million drug record samples will be used.  
The `minCellCount` is minimum number of events to report, numbers lower than this will be obscured.    


```{r executeChecks}
all_checks<-executeChecks(cdm, ingredients = 1125315)

```

We can then check what results available from ´executeChecks()´ by
```{r}
names(all_checks)
```

Let's take a look at the results. `ingredientConcepts` contains information on the concept ids that are used in the database for a given ingredient. So in the case of acetaminophen, the following drugs contain the acetaminophen as an ingredient. 



```{r,  message=FALSE, warning=FALSE }  
datatable(all_checks$ingredientConcepts,
  rownames = FALSE
)
```


After running the checks, we can write the CSV files into a zip file to disk using the `writeResultToDisk()` function. 
```{r eval=FALSE}
writeResultToDisk(all_checks,
                  databaseId = "your_database_id", 
                  outputFolder = "output_folder")
```


```{r, echo=FALSE}
  DBI::dbDisconnect(attr(cdm, "dbcon"), shutdown = TRUE)
```
