---
title: "Quantity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quantity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Run the quantity check 
```{r setup}
library(DrugExposureDiagnostics)
library(dplyr)
library(DT)

# acetaminophen concept id is 1125315
acetaminophen <- 1125315
cdm <- mockDrugExposure()
acetaminophen_checks <- executeChecks(cdm = cdm, 
                                      ingredients = acetaminophen, 
                                      checks = "quantity")
```

## Quantity Overall
This shows the quantity of the drug records summarised on ingredient level. The quantity is not a required field, but it is a most useful field. 
How the quantity is filled depends on the drug strength pattern. For quantified drugs (where the denominator_value is not missing), the quantity identifies the number of packages / items (in case of multiple dose packages). 
However, in case of non-quantified drugs (where the denominator_value is missing), the quantity identifies the volume / total number of actuations or others dispensed / prescribed. 

```{r}
datatable(acetaminophen_checks$drugQuantity,
  rownames = FALSE
)
```

| Column  | Description |
:------------- | :------------- |
ingredient_concept_id | Concept ID of ingredient. |
ingredient  | Name of drug ingredient. |
n_records | Number of records for ingredient concept. If n_records is the same as n_sample this means that there are more records but the number was cut at the pre-specified sample number for efficiency reasons. |
n_sample | The pre-specified maximum sample. If n_records is smaller than the sample it means that sampling was ignored because the total number of records was already too small. |
n_person | Number of individuals. |
minimum_drug_exposure_quantity | Minimum drug exposure quantity. |
q05_drug_exposure_quantity | 5th quantile for drug exposure quantity. |         
q10_drug_exposure_quantity | 10th quantile for drug exposure quantity. |         
q25_drug_exposure_quantity | 25th quantile for drug exposure quantity. |        
median_drug_exposure_quantity | Median drug exposure quantity. |      
q75_drug_exposure_quantity | 75th quantile for drug exposure quantity. |         
q90_drug_exposure_quantity | 90th quantile for drug exposure quantity. |     
q95_drug_exposure_quantity | 95th quantile for drug exposure quantity. |         
maximum_drug_exposure_quantity | Maximum drug exposure quantity. |  
result_obscured | TRUE if count has been suppressed due to being below the minimum cell count, otherwise FALSE. |

## Quantity by concept
This shows the quantity of the drug records on the drug concept level. The quantity is not a required field, but it is a most useful field. 
How the quantity is filled depends on the drug strength pattern. For quantified drugs (where the denominator_value is not missing), the quantity identifies the number of packages / items (in case of multiple dose packages). 
However, in case of non-quantified drugs (where the denominator_value is missing), the quantity identifies the volume / total number of actuations or others dispensed / prescribed. The tables are identical to the overall just including two more columns at the beginning. \


| Column  | Description |
:------------- | :------------- |
drug_concept_id  | ID of the drug concept. |
drug  | Name of the drug concept. |

```{r}
datatable(acetaminophen_checks$drugQuantityByConcept,
  rownames = FALSE
)
```

