---
title: "Verbatim End Date"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{VerbatimEndDate}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Run the Verbatim End Date check
The verbatim end date is the drug exposure end date in the source data. Thus, we check whether the verbatim end date equals the drug_exposure_end_date in OMOP (which is a required field).

```{r setup}
library(DrugExposureDiagnostics)
library(dplyr)
library(DT)

# acetaminophen concept id is 1125315
acetaminophen <- 1125315
cdm <- mockDrugExposure()
acetaminophen_checks <- executeChecks(
  cdm = cdm,
  ingredients = acetaminophen,
  checks = "verbatimEndDate"
)
```

## Drug verbatim end date Overall
This shows the days drug verbatim end date checks summarised on ingredient level.

```{r}
datatable(acetaminophen_checks$drugVerbatimEndDate,
  rownames = FALSE
)
```

| Column  | Description |
:------------- | :------------- |
ingredient_concept_id | Concept ID of ingredient. |
ingredient  | Name of drug ingredient. |
minimum_verbatim_end_date  | Minimum verbatim end date. |  
maximum_verbatim_end_date  | Maximum verbatim end date. |   
n_records | Number of records for ingredient concept. If n_records is the same as n_sample this means that there are more records but the number was cut at the pre-specified sample number for efficiency reasons. |
n_sample | The pre-specified maximum sample. If n_records is smaller than the sample it means that sampling was ignored because the total number of records was already too small. |
n_person | Number of individuals. |
n_missing_verbatim_end_date  | Number of records missing verbatim end date. |  
n_not_missing_verbatim_end_date  | Number of records not missing verbatim end date. |     
n_verbatim_end_date_equal_to_drug_exposure_end_date  | Number of records where verbatim end date is the same as drug exposure end date. |     
n_verbatim_end_date_and_drug_exposure_end_date_differ  | Number of records where verbatim end date and drug exposure end date differ. |   
result_obscured | TRUE if count has been suppressed due to being below the minimum cell count, otherwise FALSE. |

## Drug verbatim end date by concept
This shows the days drug verbatim end date checks on drug concept level. The tables are identical to the overall just including two more columns at the beginning. \


| Column  | Description |
:------------- | :------------- |
drug_concept_id  | ID of the drug concept. |
drug  | Name of the drug concept. |

```{r}
datatable(acetaminophen_checks$drugVerbatimEndDateByConcept,
  rownames = FALSE
)
```

